%!TEX root = Thesis.tex
\chapter{Introduction} % (fold)
\label{cha:introduction}

We all have been in a situation, in which we were driving around in a city,
trying to find a free parking space. We all know how daunting can it be to
drive numerous circles around the center of the city with a high uncertainty
about where and when we eventually find a free parking lot. With this problem
we are not alone.

\citet{rodrigue2013geography} argue in their work ``The geography of transport
systems'', that parking in the center of a modern big city with a population
bigger than one million inhabitants is one of the most prevalent transport
problems. They claim that cruising in the search for a free curb parking space
may account for more than 10\% of the local circulations as the drivers can
spend up to 20 minutes looking for a parking spot.

Several aids for supporting drivers in finding parking spaces have been
developed in the past. For example, modern garages often feature systems that
help people find a free parking space by offering a counter, that shows the
number of free parking spaces available at the moment. On-line maps usually
contain the positions of such parking garages mapped with their GPS
coordinates. This allows for these parking garages to be easily found, making
use of an ordinary SatNav device or with basically any smartphone. Even though
these occupancy counters make it easier to find a free parking spot, they only
provide the current occupancy information and not its prediction and are only
available for a small number of parking slots.

Furthermore, it is not always convenient to drive to a parking garage as
sometimes they lie far from the destination of the driver. In such cases it is
a lot more convenient to leave the car in one of the curb parking spaces.

\citet{shoup2006cruising}, while addressing the problem of adjusting parking
prices in order to reduce time spent on the search for a free parking space,
found that it took between 3.5 and 14 min to find a curb space, and that
between 8 and 74 percent of the traffic was comprised by the people cruising
for parking.

This results in having to spend time and fuel on repeatedly driving along the
same route in a desperate hope that someone has left and there is a parking
spot available now. There is significant amount of uncertainty in this task.
And uncertainty is the thing that may lead to frustration.

\citet{rodrigue2013geography} evaluates the parking difficulty by asking the
parkers to express their parking impressions. His results indicate that the
amount of parking information parkers had before their trips, was directly
related to their parking search time, which in turn, influenced their
perceptions of parking difficulty.

Dealing with such uncertainty is annoying for humans. Yet, people deal with it
much better then robotized systems. In order to carry out the parking task in
an autonomous fashion there needs to be more information provided. There must
be a deterministic algorithm, that has a decision what an optimal action is in
any moment in time. For this algorithm to function there has to be enough
information on spacial representation of the parking spaces as well as a
model, that accounts for the occupancy information.

To the extent of our knowledge, there is only a few solutions that provide
information on the positions and occupancy of the curb parking spaces.

One of the best known examples is the ``Parking on demand'' system
by~\citet{sfo,sfo2}. They present a system of parking meters that adapt the
price of curb parking spaces with relation to current occupancy in the area.
Along with intelligent parking meters they also present a smartphone
application that provides live information on the occupancy and pricing of
distinct parking spaces.

Even though this system proves to save time and money for the people that use
it, we still see a lack of autonomy in it. In order for this system to be used
in an autonomous fashion one has to introduce a planner that considers not
only spacial information but also occupancy and pricing.

Another down side of this system is its dependence on the fixed positions of
the parking meters. This implies, that in order to use the presented system we
first need to install the parking meters for every curb parking space. This
can be an effort, time and money consuming task.

We argue, that there has to be a system that will be able to map the parking
spaces, estimate their occupancy information and search for one in an optimal
and fully autonomous way.

Autonomous vehicles are becoming a topic of a great interest. In recent years,
automotive and software companies as well as the universities all over the
world have been focusing on developing their own autonomous vehicles. These
vehicles can already impressively well navigate in the
cities~\cite{stanley_auto_car,perceprion_drivec_car,lima13,daimler} and are
able to take people to an arbitrary destination even in difficult urban
environments. They also can learn how to adopt behavioral knowledge from the
traffic~\cite{behaviour_learning,spinello10:multiclass}. We believe, that
these cars are to become safer, more efficient in the means of fuel
consumption and more predictable than the human drivers. Following the recent
success of the Google self-driving car~\cite{markoff2010google} and the fact
that it is now officially allowed to use self-driving autos on public roads in
California, Nevada and Florida, USA, we predict that in the upcoming years,
people will spend less time driving by themselves and will rely more on
robotized autos.

When it comes to parking, these vehicles can find out what a parking space is
and are able to park
there~\cite{auto_cars_burgard,auto_parking09,auto_park2_11}. Despite being
able to park in an autonomous fashion, they are yet unable to know where to
search for a free parking slot by themselves and, as a consequence, where to
search for a good one.

We address precisely this issue. We present an approach that provides a system
for mapping the parking spaces by estimating their occupancy probability via
integrating information from multiple observations. Not only are we able to
estimate this information but we also present a way to plan the route in such
way that it eliminates uncertainty in finding the free parking place and
guarantees to minimize the time spent on cruising while searching for a free
parking space and walking from the found one to the destination.

\section{The Contribution of This Thesis} % (fold)
\label{sec:the_contribution_of_this_thesis}

    The task of this thesis was to develop a proof of concept system for
    supporting drivers in finding free parking spaces. The system should
    perceive cars in the environment, model parking places, and suggest
    trajectories towards parking lots.

    As result of this task, we designed such a system. Our approach requires
    only on-board sensing on a vehicle to perceive the environment. So far, we
    used a camera and a laser range finder to observe the scene and to detect
    cars from the perceptual input. This was solved by a supervised learning
    approach using a support vector machine and Histograms of Gradients  as
    features. The detections are then fused into a model of the environment
    that allows to build up a representation of the scene estimating how often
    a parking space is free or occupied.  Based on this representation, we
    define a Markov Decision Process that allows us to generate the optimal
    path, given the current knowledge, to find a parking lot and at the same
    time park as close to the desired target location as possible. The novelty
    of this thesis is a proof of concept of an integrated system, that only
    relies on on-board perception, models the parking situation and generates
    optimal trajectories for finding a parking spaces and reaching the target
    location as fast as possible.

% section the_contribution_of_this_thesis (end)

% chapter introduction (end)
